Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-11-26 manuscript.Rmd

# Could also directly import census demographic data using tidycensus package
demographic_data <- read.csv("data/DC_demographic_data.csv", header = FALSE)
names <- unlist(demographic_data[2,])
demographic_data <- demographic_data %>% 
  slice(3:8096)
head(demographic_data)
colnames(demographic_data) <- names
head(demographic_data)

#primary_secondary_roads includes interstates and other highways in DC
dc_roads <- primary_secondary_roads(state="DC") %>%
	st_transform(crs = 102285)
```

>>>>

travel_times <- travel_times %>%
	mutate(origin_id = factor(origin_id),
				 dest_id = factor(dest_id))

head(travel_times)
```

```{r}
demographic_data_big <- read.csv("DC_demographic_data.csv", header = FALSE)
names <- unlist(demographic_data_big[2,])
demographic_data_big <- demographic_data_big %>%
  slice(3:8096)
head(demographic_data_big)
colnames(demographic_data_big) <- names
demographic_data_big <- demographic_data_big %>%
  mutate(state = substr(geo2010, start = 1, stop = 2)) %>%
  mutate(tract_number = substr(geo2010, start = 10, stop = 1000))
head(demographic_data_big)

```

```{r}
#Attempting to add roads in this code chunk

library(spdep)
library(sf)
roads<-st_read("dc_roads")
#row.names(roads) <- as.character(roads$FIPSNO)
#plot(st_geometry(roads), axes=TRUE)

#tigris package - contains roads for DC
options(tigris_class="sf")
#primary_secondary_roads includes interstates and other highways in DC
dc_roads <- primary_secondary_roads(state="DC") %>%
	st_transform(crs = 102285)
```
